Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the aforementioned
effective area, point spread function (PSF), energy dispersion and residual hadronic background.
The handling of DL3 data is performed by classes and methods
in the gammapy.data  (see \ref{ssec:gammapy-data}) and the gammapy.irf
(see \ref{ssec:gammapy-irf}) subpackages.

>>>>

\gammaray data at the Data Level 3 (DL3) therefore consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the aforementioned
effective area, point spread function (PSF), energy dispersion and residual hadronic background.
The handling of DL3 data is performed by classes and methods
in the \code{gammapy.data} (see \ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see \ref{ssec:gammapy-irf}) subpackages.
